---
title: "Susceptibility summary figures"
output:
  html_document:
    keep_md: yes
    css: "css/main.css"
---

Report generated at: `r format(as.POSIXct(Sys.time(), format = "%y%m%d %H:%M"), "%m/%d/%Y %I:%M %p")` PDT

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
library(gridExtra)
library(plotly)
library(ggbeeswarm)
library(viridis)

knitr::opts_chunk$set(echo = FALSE)
source("./lib/readers.R", chdir = TRUE)
source("./lib/datatables.R", chdir = TRUE)

TABLEDIR = normalizePath(sprintf('%s/report_tables', .getpwd()))

```
## CP Figure {.tabset}

### CP indiv muts
```{r indiv-cp-iqr, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

INDIV_MUT_LIST = c(
  'N501Y',
  'E484K',
  'K417N',
  'L452R'
)

df = read.dbTable('figure_variant_indiv_cp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(variant %in% INDIV_MUT_LIST) %>%
  mutate(
    variant = factor(variant, levels=INDIV_MUT_LIST)
  )
plot = ggplot(df, aes(variant, fold)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold change (CP)")

plot1 = plot + geom_boxplot(fill="#146aa8")
plot1
```

### CP indiv muts (violin)
```{r indiv-cp-violin, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    fill="#146aa8")
plot2
```


### CP indiv muts (Jittery)
```{r indiv-cp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot + geom_quasirandom(color="#146aa8")
plot2
```

### CP indiv muts (Jittery, Boxplot)
```{r indiv-cp-iqr-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot + geom_boxplot() + geom_quasirandom(color="#146aa8")
plot3
```


### CP combo muts
```{r combo-cp-iqr, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

COMBO_MUT_LIST = c(
  'B.1.1.7',
  'B.1.351',
  'P.1',
  'B.1.427/9'
)

df = read.dbTable('figure_variant_combo_cp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(nickname %in% COMBO_MUT_LIST)  %>%
  mutate(
    nickname = factor(nickname, levels=COMBO_MUT_LIST)
  )
plot = ggplot(df, aes(nickname, fold)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold change (CP)")

plot1 = plot + geom_boxplot(fill="#146aa8")
plot1
```

### CP combo muts (Jittery)
```{r combo-cp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot + geom_quasirandom(color="#146aa8")
plot2
```

### CP combo muts (violin)
```{r combo-cp-violin, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    fill="#146aa8")
plot2
```

### CP combo muts (Jittery, Boxplot)
```{r combo-cp-iqr-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot + geom_boxplot() + geom_quasirandom(color="#146aa8")
plot3
```


## VP Figure {.tabset}

### VP indiv muts
```{r indiv-vp-iqr, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

VACCINE_LIST = c(
  "BNT162b2",
  "mRNA-1273",
  "AZD1222",
  "NVX-CoV2373",
  "Sptunik V",
  "CoronaVac",
  "BBIBP-CorV",
  "BBV152"
)

IGNORE_VACCINE_LIST = c(
  "mRNA-1273.351",
  "mRNA-1273.211",
  "mRNA-1273 + mRNA-1273.351"
)

INDIV_MUT_LIST = c(
  'N501Y',
  'E484K',
  'K417N',
  'L452R'
)

df = read.dbTable('figure_variant_indiv_vp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(variant %in% INDIV_MUT_LIST) %>%
  filter(vaccine %in% VACCINE_LIST) %>%
  mutate(
    variant = factor(variant, levels=INDIV_MUT_LIST),
    vaccine = factor(vaccine, levels=VACCINE_LIST)
  )
plot = ggplot(df, aes(variant, fold, fill=vaccine)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  # scale_fill_brewer(palette="Spectral") +
  scale_fill_viridis(discrete=TRUE) + 
  scale_color_viridis(discrete=TRUE) + 
  # scale_color_brewer(palette="Spectral") +
  theme(
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold change (VP)")

plot1 = plot + geom_boxplot(position = position_dodge(preserve = "single"))
plot1
```

### VP indiv muts (Jittery)
```{r indiv-vp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  # geom_boxplot(position = position_dodge2(preserve = "single")) +
  # geom_point(pch=21, position=position_jitterdodge())
  geom_quasirandom(aes(color=vaccine), dodge.width=1)
plot2
```

### VP indiv muts (Violin)

```{r indiv-vp-violin, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot2
```


### VP combo muts
```{r combo-vp-iqr, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

COMBO_MUT_LIST = c(
  'B.1.1.7',
  'B.1.351',
  'P.1',
  'B.1.427/9'
)

df = read.dbTable('figure_variant_combo_vp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(nickname %in% COMBO_MUT_LIST) %>%
  filter(vaccine %in% VACCINE_LIST) %>%
  mutate(
    nickname = factor(nickname, levels=COMBO_MUT_LIST),
    vaccine = factor(vaccine, levels=VACCINE_LIST)
  )
plot = ggplot(df, aes(nickname, fold, fill=vaccine)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  # scale_fill_brewer(palette="Spectral") +
  scale_fill_viridis(discrete=TRUE) + 
  scale_color_viridis(discrete=TRUE) + 
  # scale_color_brewer(palette="Spectral") + 
  theme(
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold change (VP)")

plot1 = plot +
  geom_boxplot(position = position_dodge2(preserve = "single"))
plot1
```

### VP combo muts (Jittery)
```{r combo-vp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  # geom_boxplot(position = position_dodge2(preserve = "single")) +
  # geom_point(pch=21, position=position_jitterdodge(0.25))
  geom_quasirandom(aes(color=vaccine), dodge.width=1)
plot2
```

### VP indiv muts (Violin)

```{r combo-vp-violin, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot2
```

## Plasmas Figure {.tabset}

### CP and VP summary
```{r cpvp, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plasmaDT = read.dbTable('figure_plasma.csv', tables_dir=TABLEDIR) %>%
  mutate(
    study = ifelse(study=='vac', 'Vaccine', 'CP'),
    variant = ifelse(variant == "B.1.429/B.1.427", "B.1.427/429", variant)
    ) %>%
  filter(
    variant != 'L452R' & variant != "B.1.526"
  )

VARIANT = c(
  "B.1.1.7",
  "B.1.351",
  "P.1",
  "B.1.427/9",
  # "B.1.526",
  "N501Y",
  "E484K",
  "K417N",
  "N439K",
  # "L452R",
  "Y453F",
  "∆69/70",
  "∆144"
)

SUSC_VALUE = c("R", "I", "S")
STUDY_TYPE = c("CP", "Vaccine")

plots = list()
i = 1

for (st in STUDY_TYPE) {
    dfPlot = plasmaDT %>%
      filter(study == st) %>%
      mutate(
        variant = factor(variant, VARIANT),
        susc = factor(susc, SUSC_VALUE)
      )

    dfAgg = dfPlot %>%
      group_by(variant, num_study) %>%
      summarise(total=sum(sample_num)) %>%
      mutate(
        total_label = ifelse(
          num_study > 1,
          yes=sprintf('%s studies', num_study),
          no=sprintf('%s study', num_study)
        )

      )

    p <- ggplot(data=dfPlot, aes(x=variant, y=sample_num)) +
      geom_bar(
        aes(fill=susc),
        size=0.2,
        color="#000000",
        stat="identity",
        position='stack'
      ) +
      scale_fill_manual(values = c(
        'R' = "#146aa8",
        'I' = "#7fcbee",
        'S' = "#ffffff"
      )) +
      scale_y_continuous(
        expand=expansion(mult = c(0, .1))
        ) +
      geom_text(
        data=dfAgg,
        aes(y=total, label=total_label),
        size = 4.6,
        vjust = -0.5
        ) +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      ylab("# Samples")

    if (st == 'CP') {
      figLabel = "Convalescent plasma"
    }
    else {
      figLabel = "Plasma from vaccinated persons"
    }
    # p = p + ggtitle("Convalescent plasma")
    p = p + annotate(
          "text",
          y= Inf,
          x = Inf,
          label=figLabel,
          size=8,
          vjust=2,
          hjust=1.1)

    plots[[i]] = p
    i = i + 1
}

grid.arrange(grobs = plots)
```

## DMS  {.tabset}

### DMS vs fold
```{r dms-fold, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}
df = read.dbTable('summary_dms.csv', tables_dir=TABLEDIR) %>%
  mutate(
    susceptible_level=ifelse(
        fold < 3, 'susceptible', ifelse(fold < 10, 'partial-resistance', 'resistant'))
  )
ggplot(data=df, aes(
        x=fold, y=score,
        color=susceptible_level)) +
      geom_point(size=2) +
      # geom_text(size=3, vjust=-1) +
      scale_x_continuous(
        trans='log10',
        breaks=c(1, 3, 10, 100, 1000, 10000)
      ) +
      scale_y_continuous(
        breaks=c(0.01, 0.06, 0.1, 0.25, 0.5, 1),
        expand=c(0,0)
      ) +
      geom_hline(
        yintercept = 0.01,
        linetype="dashed",
        color = "blue") +
      geom_hline(
        yintercept = 0.1,
        linetype="dashed",
        color = "blue") +
      geom_hline(
        yintercept = 0.06,
        linetype="dashed",
        color = "blue") +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      xlab("Fold change") +
      ylab("DMS Score")
```

### DMS vs fold 3D
```{r dms-fold-3d, out.width="100%", message=FALSE, warning=FALSE, echo=FALSE}
plot_ly(df, x=~fold, y=~score, z=~position)  %>%
  layout(
    scene =list(
      xaxis = list(
        type = "log",
        nticks=6
        )
    )
  ) %>%
  add_markers(color = ~susceptible_level)
```

### DMS vs fold by mab
```{r dms-fold-mab, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plots = list()
i = 1

for (ab in unique(df$mab)) {
  dfPlot = df %>%
    filter(mab == ab)

  plot = ggplot(dfPlot, aes(x=fold, y=score, color=susceptible_level)) +
      geom_point(size=2) +
      scale_x_continuous(
        trans='log10',
        breaks=c(1, 3, 10, 100, 1000, 10000)
      ) +
      scale_y_continuous(
        breaks=c(0, 0.25, 0.5, 1),
        expand=c(0,0)
      ) +
      geom_hline(
        aes(yintercept = 0.1),
        linetype="dashed",
        color = "blue") +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.text.y = element_blank(),
        strip.background = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      xlab(paste("Fold change:", ab)) +
      ylab("DMS Score")

  plots[[i]] = plot
  i = i + 1
}

grid.arrange(grobs = plots, ncol=4)

```

## DMS Statistic Test  {.tabset}

### All
```{r dms-fold-st-all}
df = read.dbTable('summary_dms.csv', tables_dir=TABLEDIR) %>%
  mutate(
    susceptible_level=ifelse(
        fold < 3, 'susceptible', ifelse(fold < 10, 'partial-resistance', 'resistant'))
  )
tbl = table(df$fold, df$score)
chisq.test(tbl)

result = cor.test(df$fold, df$score, method="spearman", exact = FALSE)
print(result)
```

### Fold >= 10 and score >= 0.1
```{r dms-fold-st-10-01}
df_Fold_gt10 = df %>%
  filter(
    fold >= 10 & score >= 0.1
  )
tbl = table(df_Fold_gt10$fold, df_Fold_gt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_gt10$fold, df_Fold_gt10$score, method="spearman", exact = FALSE)
print(result)
```

### Fold >= 10
```{r dms-fold-st-gt-10}
df_Fold_gt10 = df %>%
  filter(
    fold >= 10
  )
tbl = table(df_Fold_gt10$fold, df_Fold_gt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_gt10$fold, df_Fold_gt10$score, method="spearman", exact = FALSE)
print(result)
```

### Fold < 10
```{r dms-fold-st-lt-10}
df_Fold_lt10 = df %>%
  filter(
    fold < 10
  )
tbl = table(df_Fold_lt10$fold, df_Fold_lt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_lt10$fold, df_Fold_lt10$score, method="spearman", exact = FALSE)
print(result)
```


### Fold >10 and score < 0.1
```{r dms-fold-st-10-01-outliner}
df_Score_outlier = df %>%
  filter(
    score <= 0.1 & fold >= 10
  )
tbl = table(df_Score_outlier$fold, df_Score_outlier$score)
chisq.test(tbl)

result = cor.test(df_Score_outlier$fold, df_Score_outlier$score, method="spearman", exact = FALSE)
print(result)
```


### Mab, Score
```{r dms-fold-st-mab-score}
tbl = table(df$mab, df$score)
chisq.test(tbl)

```
