---
title: "Susceptibility summary figures"
output:
  html_document:
    keep_md: yes
    css: "css/main.css"
---

Report generated at: `r format(as.POSIXct(Sys.time(), format = "%y%m%d %H:%M"), "%m/%d/%Y %I:%M %p")` PDT

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(gridExtra)
library(plotly)
library(ggbeeswarm)
library(viridis)

knitr::opts_chunk$set(
  echo = FALSE,
  dev = c("png", "svg")
)
source("./lib/readers.R", chdir = TRUE)
source("./lib/datatables.R", chdir = TRUE)

TABLEDIR = normalizePath(sprintf('%s/report_tables', .getpwd()))

```
## CP Figure {.tabset}

### CP indiv muts
```{r indiv-cp-iqr, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

INDIV_MUT_LIST = c(
  'N501Y',
  'E484K',
  'K417N',
  'L452R'
)

df = read.dbTable('figure_variant_indiv_cp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(pattern %in% INDIV_MUT_LIST) %>%
  mutate(
    pattern = factor(pattern, levels=INDIV_MUT_LIST)
  )
plot = ggplot(df, aes(pattern, fold)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold reduced neutralization (CP)")

plot1 = plot + geom_boxplot(fill="#146aa8")
plot1
```

### CP indiv muts (violin)
```{r indiv-cp-violin, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    fill="#146aa8")
plot2
```


### CP indiv muts (Jittery)
```{r indiv-cp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot + geom_quasirandom(color="#146aa8")
plot2
```

### CP indiv muts (Jittery, Boxplot)
```{r indiv-cp-iqr-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot + geom_boxplot() + geom_quasirandom(color="#146aa8")
plot3
```


### CP combo muts
```{r combo-cp-iqr, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

COMBO_MUT_LIST = c(
  'Alpha',
  'Beta',
  'Gamma',
  'Epislon'
)

df = read.dbTable('figure_variant_combo_cp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(var_name %in% COMBO_MUT_LIST)  %>%
  mutate(
    var_name = factor(var_name, levels=COMBO_MUT_LIST)
  )
plot = ggplot(df, aes(var_name, fold)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold reduced neutralization (CP)")

plot1 = plot + geom_boxplot(fill="#146aa8")
plot1
```

### CP combo muts (Jittery)
```{r combo-cp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot + geom_quasirandom(color="#146aa8")
plot2
```

### CP combo muts (violin)
```{r combo-cp-violin, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}

plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    fill="#146aa8")
plot2
```

### CP combo muts (Jittery, Boxplot)
```{r combo-cp-iqr-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot + geom_boxplot() + geom_quasirandom(color="#146aa8")
plot3
```


## VP Figure {.tabset}

### VP indiv muts
```{r indiv-vp-iqr, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

VACCINE_LIST = c(
  "BNT162b2",
  "mRNA-1273",
  "AZD1222",
  "NVX-CoV2373",
  "Sputnik V",
  "CoronaVac",
  "BBIBP-CorV",
  "BBV152"
)

VACCINE_TYPE_LIST = c(
  'mRNA',
  'Viral vector',
  'Inactivated virus',
  'Protein subunit'
)

IGNORE_VACCINE_LIST = c(
  "mRNA-1273.351",
  "mRNA-1273.211",
  "mRNA-1273 + mRNA-1273.351"
)

INDIV_MUT_LIST = c(
  'N501Y',
  'E484K',
  'K417N',
  'L452R'
)

df = read.dbTable('figure_variant_indiv_vp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(pattern %in% INDIV_MUT_LIST) %>%
  filter(vaccine %in% VACCINE_LIST) %>%
  mutate(
    pattern = factor(pattern, levels=INDIV_MUT_LIST),
    vaccine = factor(vaccine, levels=VACCINE_LIST),
    vaccine_type = factor(vaccine_type, levels=VACCINE_TYPE_LIST),
  )
plot = ggplot(df, aes(pattern, fold)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  scale_fill_brewer(palette="Dark2") +
  scale_color_brewer(palette="Dark2") +
  # scale_fill_viridis(discrete=TRUE) +
  # scale_color_viridis(discrete=TRUE) +
  theme(
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold reduced neutralization (VP)")

plot1 = plot + 
  geom_boxplot(
    fill="#146aa8",
    position = position_dodge(preserve = "single")
    )
plot1
```

### VP indiv muts (Jittery)
```{r indiv-vp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  # geom_boxplot(position = position_dodge2(preserve = "single")) +
  # geom_point(pch=21, position=position_jitterdodge())
  geom_quasirandom(aes(color=vaccine), dodge.width=1)
plot2
```

### VP indiv muts (Violin)

```{r indiv-vp-violin, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  geom_violin(
    aes(fill=vaccine),
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot2
```

### VP indiv By vaccine type

```{r indiv-vp-violin-vp-type, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot +
  geom_violin(
    aes(fill=vaccine_type),
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot3
```


### VP combo muts
```{r combo-vp-iqr, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

COMBO_MUT_LIST = c(
  'Alpha',
  'Beta',
  'Gamma',
  'Delta'
)

df = read.dbTable('figure_variant_combo_vp.csv', tables_dir=TABLEDIR)
df = df %>%
  filter(var_name %in% COMBO_MUT_LIST) %>%
  filter(vaccine %in% VACCINE_LIST) %>%
  mutate(
    var_name = factor(var_name, levels=COMBO_MUT_LIST),
    vaccine = factor(vaccine, levels=VACCINE_LIST),
    vaccine_type = factor(vaccine_type, levels=VACCINE_TYPE_LIST),
  )
plot = ggplot(df, aes(var_name, fold, fill=vaccine)) +
  scale_y_continuous(
    trans='log10',
    breaks=c(1, 3, 10, 100, 1000, 10000)
    ) +
  scale_fill_brewer(palette="Dark2") +
  scale_color_brewer(palette="Dark2") +
  # scale_fill_viridis(discrete=TRUE) +
  # scale_color_viridis(discrete=TRUE) +
  theme(
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
  ylab("Fold reduced neutralization (VP)")

plot1 = plot +
  geom_boxplot(position = position_dodge2(preserve = "single"))
plot1
```

### VP combo muts (Jittery)
```{r combo-vp-jitter, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  # geom_boxplot(position = position_dodge2(preserve = "single")) +
  # geom_point(pch=21, position=position_jitterdodge(0.25))
  geom_quasirandom(aes(color=vaccine), dodge.width=1)
plot2
```

### VP combo muts (Violin)

```{r combo-vp-violin, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
plot2 = plot +
  geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot2
```

### VP combo By vaccine type

```{r combo-vp-violin-vp-type, fig.height=5, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plot3 = plot +
  geom_violin(
    aes(fill=vaccine_type),
    draw_quantiles = c(0.25, 0.5, 0.75),
    scale="width"
    )
plot3
```


## DMS  {.tabset}

### DMS vs fold
```{r dms-fold, fig.height=5, fig.retina=4, fig.width=5, message=FALSE, warning=FALSE, echo=FALSE}
df = read.dbTable('summary_dms.csv', tables_dir=TABLEDIR) %>%
  mutate(
    susceptible_level=ifelse(
        fold < 3, 'susceptible', ifelse(fold < 10, 'partial-resistance', 'resistant'))
  )
ggplot(data=df, aes(
        x=fold, y=score,
        color=susceptible_level)) +
      geom_point(size=2) +
      # geom_text(size=3, vjust=-1) +
      scale_x_continuous(
        trans='log10',
        breaks=c(1, 3, 10, 100, 1000, 10000)
      ) +
      scale_y_continuous(
        breaks=c(0.1, 0.5, 1),
        expand=c(0,0)
      ) +
      # geom_hline(
      #   yintercept = 0.01,
      #   linetype="dashed",
      #   color = "blue") +
      geom_hline(
        yintercept = 0.1,
        linetype="dashed",
        color = "blue") +
      # geom_hline(
      #   yintercept = 0.06,
      #   linetype="dashed",
      #   color = "blue") +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      xlab("Fold reduced neutralization") +
      ylab("Escape fraction")
```

### DMS vs fold 3D
```{r dms-fold-3d, out.width="100%", message=FALSE, warning=FALSE, echo=FALSE}
plot_ly(df, x=~fold, y=~score, z=~position)  %>%
  layout(
    scene =list(
      xaxis = list(
        type = "log",
        nticks=6
        )
    )
  ) %>%
  add_markers(color = ~susceptible_level)
```

### DMS vs fold by mab
```{r dms-fold-mab, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
EUA_MABS = c(
  'Bamlanivimab',
  'Etesevimab',
  'Casirivimab',
  'Imdevimab',
  'Cilgavimab',
  'Tixagevimab',
  'Vir-7831',
  'C135',
  'C144'
)

plots = list()
i = 1

for (ab in EUA_MABS) {
  dfPlot = df %>%
    filter(mab == ab)

  plot = ggplot(dfPlot, aes(x=fold, y=score, color=susceptible_level)) +
      geom_point(size=2) +
      scale_x_continuous(
        trans='log10',
        breaks=c(1, 3, 10, 100, 1000, 10000),
        limits = c(0.1, 10000)
      ) +
      scale_y_continuous(
        breaks=c(0, 0.25, 0.5, 1),
        expand=c(0, 0),
        limits=c(0, 1)
      ) +
      scale_color_manual(
        values = c(
        'resistant' = "#D55E00",
        'partial-resistance' = "#0072B2",
        'susceptible' = "#009E73"
      )
      ) +
      geom_hline(
        aes(yintercept = 0.1),
        linetype="dashed",
        color = "blue") +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.text.y = element_blank(),
        strip.background = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      xlab(ab) +
      ylab("Escape fraction")

  plots[[i]] = plot
  i = i + 1
}

grid.arrange(grobs = plots, ncol=3)

```

### DMS no fold
```{r dms-missing-fold, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}
df = read.dbTable('summary_dms_missing_fold.csv', tables_dir=TABLEDIR)

plots = list()
i = 1

for (ab in EUA_MABS) {
  dfPlot = df %>%
    filter(mab == ab)

  plot = ggplot(dfPlot, aes(x=position, y=score, color=amino_acid)) +
      geom_point(size=0.5) +
      scale_y_continuous(
        breaks=c(0, 0.25, 0.5, 1),
        expand=c(0, 0),
        limits=c(0, 1)
      ) +
      geom_hline(
        aes(yintercept = 0.1),
        linetype="dashed",
        color = "blue") +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(size=10),
        axis.text.y = element_blank(),
        strip.background = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      xlab(ab) +
      ylab("Escape fraction")

  plots[[i]] = plot
  i = i + 1
}

grid.arrange(grobs = plots, ncol=3)
```

## DMS Statistic Test  {.tabset}

### All
```{r dms-fold-st-all}
df = read.dbTable('summary_dms.csv', tables_dir=TABLEDIR) %>%
  mutate(
    susceptible_level=ifelse(
        fold < 3, 'susceptible', ifelse(fold < 10, 'partial-resistance', 'resistant'))
  )
tbl = table(df$fold, df$score)
chisq.test(tbl)

result = cor.test(df$fold, df$score, method="spearman", exact = FALSE)
print(result)
```

### Fold >= 10 and score >= 0.1
```{r dms-fold-st-10-01}
df_Fold_gt10 = df %>%
  filter(
    fold >= 10 & score >= 0.1
  )
tbl = table(df_Fold_gt10$fold, df_Fold_gt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_gt10$fold, df_Fold_gt10$score, method="spearman", exact = FALSE)
print(result)
```

### Fold >= 10
```{r dms-fold-st-gt-10}
df_Fold_gt10 = df %>%
  filter(
    fold >= 10
  )
tbl = table(df_Fold_gt10$fold, df_Fold_gt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_gt10$fold, df_Fold_gt10$score, method="spearman", exact = FALSE)
print(result)
```

### Fold < 10
```{r dms-fold-st-lt-10}
df_Fold_lt10 = df %>%
  filter(
    fold < 10
  )
tbl = table(df_Fold_lt10$fold, df_Fold_lt10$score)
chisq.test(tbl)


result = cor.test(df_Fold_lt10$fold, df_Fold_lt10$score, method="spearman", exact = FALSE)
print(result)
```


### Fold >10 and score < 0.1
```{r dms-fold-st-10-01-outliner}
df_Score_outlier = df %>%
  filter(
    score <= 0.1 & fold >= 10
  )
tbl = table(df_Score_outlier$fold, df_Score_outlier$score)
chisq.test(tbl)

result = cor.test(df_Score_outlier$fold, df_Score_outlier$score, method="spearman", exact = FALSE)
print(result)
```


### Mab, Score
```{r dms-fold-st-mab-score}
tbl = table(df$mab, df$score)
chisq.test(tbl)

```

## Variant summary {.tabset}

### Indiv summary (without distinguish study type)
```{r indiv-mutations, fig.height=15, fig.retina=4, fig.width=15, message=FALSE, warning=FALSE, echo=FALSE}

MIN_SAMPLES = 10

df = read.dbTable('summary_variant_indiv.csv', tables_dir=TABLEDIR) %>%
  mutate(
    samples=CP + VP + all.mAbs
  ) %>%
  filter(
    samples > MIN_SAMPLES
  )

plots = list()
i = 1

for (d in unique(df$Domain)) {
  dfPlot = df %>%
    filter(Domain == d)

  p <- ggplot(dfPlot, aes(x=reorder(pattern, Position), y=samples)) +
      geom_bar(
        stat='identity',
        width=0.01 * length(unique(dfPlot$pattern)),
        fill="#146aa8"
        ) +
      scale_y_continuous(
        expand=expansion(mult = c(0, .1))
        ) +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size=12, angle=45, hjust=1),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      annotate(
          "text",
          y=Inf,
          x=Inf,
          label=d,
          size=10,
          vjust=2,
          hjust=1.1
          )
  plots[[i]] = p
  i = i + 1

}

grid.arrange(grobs = plots, ncol=1)

```

### Indiv summary (distinguish by study type)
```{r indiv-mutations-study-type, fig.height=15, fig.retina=4, fig.width=15, message=FALSE, warning=FALSE, echo=FALSE}

STUDY_TYPE_ORDER = c(
  "CP",
  "VP",
  "mAb"
)

df = read.dbTable('summary_variant_indiv.csv', tables_dir=TABLEDIR) %>%
  mutate(
    samples=CP + VP + all.mAbs
  ) %>%
  filter(
    samples > MIN_SAMPLES
  )

dfCP = df %>%
  select(
    pattern,
    Position,
    Domain,
    samples=CP
  ) %>%
  mutate(
    study_type=factor("CP", levels=STUDY_TYPE_ORDER)
  )

dfVP = df %>%
  select(
    pattern,
    Position,
    Domain,
    samples=VP
  ) %>%
  mutate(
    study_type=factor("VP", levels=STUDY_TYPE_ORDER)
  )

dfMAb = df %>%
  select(
    pattern,
    Position,
    Domain,
    samples=all.mAbs
  ) %>%
  mutate(
    study_type=factor("mAb", levels=STUDY_TYPE_ORDER)
  )

df = bind_rows(dfCP, dfVP, dfMAb)

plots = list()
i = 1

for (d in unique(df$Domain)) {
  dfPlot = df %>%
    filter(Domain == d)

  p <- ggplot(dfPlot, aes(x=reorder(pattern, Position), y=samples)) +
      geom_bar(
        aes(fill=study_type),
        stat='identity',
        width=0.01 * length(unique(dfPlot$pattern)),
        position = 'stack'
        ) +
      scale_y_continuous(
        expand=expansion(mult = c(0, .1))
        ) +
      # scale_fill_viridis(discrete = TRUE) +
      scale_fill_brewer(palette = "Dark2") +
      # labs(fill="Study type") +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size=12, angle=45, hjust=1),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      annotate(
          "text",
          y=Inf,
          x=Inf,
          label=d,
          size=10,
          vjust=2,
          hjust=1.1
          )
  plots[[i]] = p
  i = i + 1

}

grid.arrange(grobs = plots, ncol=1)

```

### Domain summary

```{r indiv-domain-study-type, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

DOMAINS = c(
  'NTD',
  'RBD',
  'CTD',
  'S2'
)

get_domain_table = function(table, treatment) {
  table = table %>%
    mutate(
      Domain=factor(Domain, levels=DOMAINS)
    ) %>%
    select(
      Domain,
      S,
      I,
      R
    ) %>%
    group_by(
      Domain
    ) %>%
    summarise(
      S_samples=sum(S),
      I_samples=sum(I),
      R_samples=sum(R)
    ) %>%
    pivot_longer(
      cols=ends_with('samples'),
      names_to="category",
      values_to="samples"
    ) %>%
    mutate(
      category=factor(category, levels=c('R_samples','I_samples', 'S_samples')),
      treatment=treatment
    )
  table
}

get_domain_plot <- function(table) {
  plot <- ggplot(table, aes(x=Domain, y=samples, fill=category)) +
      geom_bar(
        stat = "identity",
        width = 0.4,
        color = "#000000"
      ) +
      facet_grid(cols=vars(treatment)) +
      scale_y_continuous(
        expand=expansion(
          mult = c(0, .1))
      ) +
      scale_fill_manual(values = c(
        'R_samples' = "#146aa8",
        'I_samples' = "#7fcbee",
        'S_samples' = "#ffffff"
      )) +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_text(size=20),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        )
      # annotate(
      #     "text",
      #     y=Inf,
      #     x=Inf,
      #     label=treatment,
      #     size=10,
      #     vjust=2,
      #     hjust=1.1
      #     )
  plot
}

dfCP = read.dbTable('summary_variant_indiv_cp.csv', tables_dir=TABLEDIR)
dfCP = get_domain_table(dfCP, 'CP')
dfVP = read.dbTable('summary_variant_indiv_vp.csv', tables_dir=TABLEDIR)
dfVP =get_domain_table(dfVP, 'VP')
dfMAb = read.dbTable('summary_variant_indiv_mab.csv', tables_dir=TABLEDIR)
dfMAb = get_domain_table(dfMAb, 'MAb')

table = bind_rows(dfCP, dfVP, dfMAb)

plot = get_domain_plot(table)
plot
# plots = list()
# plots[[1]] = get_domain_plot(dfCP, 'CP')
# plots[[2]] = get_domain_plot(dfVP, 'VP')
# plots[[3]] = get_domain_plot(dfMAb, 'MAb')
#
# grid.arrange(grobs = plots, ncol=1)

```


### Variant summary (distinguish by study type)
```{r combo-mutations-study-type, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

NICKNAME_LIST = c(
  'Alpha',
  'Alpha/E484K',
  'Beta',
  'Gamma',
  'Delta'
)

df = read.dbTable('summary_variant_combo.csv', tables_dir=TABLEDIR) %>%
  filter(
    var_name %in% NICKNAME_LIST
  ) %>%
  select(
    var_name,
    CP,
    VP,
    all.mAbs
  ) %>%
  group_by(
    var_name
  ) %>%
  summarise(
    CP=sum(CP),
    VP=sum(VP),
    all.mAbs=sum(all.mAbs)
  ) %>%
  mutate(
    samples=CP + VP + all.mAbs,
    var_name=factor(var_name, levels=NICKNAME_LIST)
  )

dfCP = df %>%
  select(
    var_name,
    samples=CP
  ) %>%
  mutate(
    study_type=factor("CP", levels=STUDY_TYPE_ORDER)
  )

dfVP = df %>%
  select(
    var_name,
    samples=VP
  ) %>%
  mutate(
    study_type=factor("VP", levels=STUDY_TYPE_ORDER)
  )

dfMAb = df %>%
  select(
    var_name,
    samples=all.mAbs
  ) %>%
  mutate(
    study_type=factor("mAb", levels=STUDY_TYPE_ORDER)
  )

df = bind_rows(dfCP, dfVP, dfMAb)

plots = list()
i = 1

for (s in unique(df$study_type)) {
  dfPlot = df %>%
    filter(study_type == s)

  p <- ggplot(dfPlot, aes(x=var_name, y=samples)) +
      geom_bar(
        stat='identity',
        fill="#146aa8"
        ) +
      scale_y_continuous(
        expand=expansion(
          mult = c(0, .1)
          ),
        limits = c(0, 800)
        ) +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size=15, angle=45, hjust=1),
        axis.text.y = element_text(size=15),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      annotate(
          "text",
          y=Inf,
          x=Inf,
          label=s,
          size=10,
          vjust=2,
          hjust=1.1
          )
  plots[[i]] = p
  i = i + 1

}

grid.arrange(grobs = plots, ncol=1)

```
