---
title: "Resistance data tables"
output:
  html_document:
    css: "css/main.css"
---

Report generated at: `r format(as.POSIXct(Sys.time(), format = "%y%m%d %H:%M"), "%m/%d/%Y %I:%M %p")` PDT

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(stringr)
knitr::opts_chunk$set(echo = FALSE)
source("./lib/readers.R", chdir = TRUE)
source("./lib/datatables.R", chdir = TRUE)


partialResistFold = 3
resistFold = 10
dfSuscResultsMAb = read.suscResultsMAb(withExcluded = TRUE)
dfSuscResultsCP = read.suscResultsCP(
  partialResistFold = partialResistFold,
  resistFold = resistFold,
  withExcluded = TRUE
)
dfSuscResultsIP = read.suscResultsIP(
  partialResistFold = partialResistFold,
  resistFold = resistFold,
  withExcluded = TRUE
)
dfSuscResultsCP$group = "CP"
dfSuscResultsIP$group = "IP"
dfSuscResultsPlasma = bind_rows(dfSuscResultsCP, dfSuscResultsIP)
dfVirusVariants = read.virusVariants() %>%
  select(variant_name, num_muts, expandable, spike_muts)
dfArticles = read.articles()
dfVariantMutations = read.variantMutations()

dfSuscResultsMAb = dfSuscResultsMAb %>%
  inner_join(
    dfVirusVariants,
    by = "variant_name",
    suffix = c(".susc", ".variant")
  ) %>%
  inner_join(
    dfArticles,
    by = "ref_name",
    suffix = c(".susc", ".ref")
  )

dfSuscResultsPlasma = dfSuscResultsPlasma %>%
  inner_join(
    dfVirusVariants,
    by = "variant_name",
    suffix = c(".susc", ".variant")
  ) %>%
  inner_join(
    dfArticles,
    by = "ref_name",
    suffix = c(".susc", ".ref")
  )
```

<!-- ## Individual spike mutations / mAb neutralization -->

<!-- Columns explained: -->

<!-- - __Author__: Internal unique reference identifier -->
<!-- - __DOI__: DOI -->
<!-- - __Source__: Location of data within reference -->
<!-- - __Date__: Date data added to database -->
<!-- - __mAb__: mAb name or abbreviation -->
<!-- - __Position__: Spike amino acid position -->
<!-- - __AA__: Amino acid difference from Wuhan reference sequence (Genbank accession NC_045512.2) -->
<!-- - __Control__: Variant used in control group -->
<!-- - __FoldCmp__: Modifier of estimate of fold difference from the control "wildtype" virus: <, >, ~ -->
<!-- - __Fold__: Fold difference from the control "wildtype" virus -->
<!-- - __Assay__: Default assay is pseudovirus. Assays performed using "authentic" virus are indicated -->
<!-- - __Include__: Entries containing "Exclude" are not displayed on the web -->

<!-- You can copy, download, or print the table using buttons below: -->

```{r phenotypes-mut-mab}

# dfSuscResultsMAb %>%
#   filter(num_muts == 1) %>%
#   inner_join(
#     dfVariantMutations,
#     by = "variant_name",
#     suffix = c(".susc", ".variantMut")
#   ) %>%
#   mutate(
#     DOI = ifelse(is.na(doi), url, doi),
#     mAb = Vectorize(function(x) paste0(x, collapse = "+"))(short_ab_name_with_author_target),
#     FoldCmp = ifelse(fold_cmp == "=", "", fold_cmp),
#     Fold = ifelse(is.na(fold), "", fold),
#     Assay = ifelse(is.na(assay), "", assay),
#     Include = ifelse(include, "Yes", "No"),
#     Control = ifelse(control_variant_name == 'Control', "", control_variant_name)
#   ) %>%
#   select(
#     Author = ref_name,
#     DOI,
#     Source = section,
#     Date = date_added.susc,
#     mAb,
#     Position = position,
#     AA = amino_acid,
#     Control,
#     FoldCmp,
#     Fold,
#     Assay,
#     Include
#   ) %>%
#   arrange(
#     Author,
#     Position,
#     AA,
#     mAb
#   ) %>%
#   styledDT
```

<!-- ## Individual spike mutations / plasma neutralization -->

<!-- Columns explained: -->

<!-- - __Author__: Internal unique reference identifier -->
<!-- - __DOI__: DOI -->
<!-- - __Source__: Location of data within reference -->
<!-- - __Date__: Date data added to database -->
<!-- - __Plasma__: CP (convalescent plasma), BNT162b2 (BNT162b2 vaccinated persons), mRNA-1273 (mRNA-1273 vaccinated persons), NVX-CoV2373 (NVX-CoV2373 vaccinated persons). For some CP, author-defined disease severity is provided (e.g., Mild, Hospitalized). For some samples, time since convalescence or vaccination is provided in weeks or months (e.g. 4W, 8M) -->
<!-- - __Vaccine__: Vaccine name -->
<!-- - __Infection__: Infected variant -->
<!-- - __Position__: Spike amino acid position -->
<!-- - __AA__: Amino acid difference from Wuhan reference sequence (Genbank accession NC_045512.2) -->
<!-- - __Control__: Variant used in control group -->
<!-- - __FoldCmp__: Modifier of estimate of fold difference from the control "wildtype" virus: <, >, ~ -->
<!-- - __Fold__: Fold difference from the control "wildtype" virus -->
<!-- - __Level__: Susceptibility level -->
<!-- - __Assay__: Default assay is pseudovirus. Assays performed using "authentic" virus are indicated -->
<!-- - __Count__: For some studies, data are presented in aggregate. In this case, the count indicates the number of experiments having the same entries in the Foldcmp and Fold columns. -->
<!-- - __Include__: Entries containing "Exclude" are not displayed on the web -->

<!-- You can copy, download, or print the table using buttons below: -->

```{r phenotypes-mut-plasma}

# dfMutPlasma = dfSuscResultsPlasma %>%
#   filter(num_muts == 1) %>%
#   inner_join(
#     dfVariantMutations,
#     by = "variant_name",
#     suffix = c(".susc", ".variantMut")
#   )
# dfMutPlasma$resistance_level = as.character(dfMutPlasma$resistance_level)
# dfMutPlasma %>%
#   mutate(
#     DOI = ifelse(is.na(doi), url, doi),
#     Plasma = Vectorize(function(refName, rxName, variantName, ordNum) {
#       total = nrow(filter(dfMutPlasma, rx_name == rxName & ref_name == refName & variant_name == variantName))
#       ifelse(
#         total == 1,
#         yes = rxName,
#         no = sprintf(sprintf("%%s:%%0%dd", 1 + floor(log(total, 10))), rxName, ordNum)
#       )
#     })(ref_name, rx_name, variant_name, ordinal_number),
#     Vaccine = ifelse(is.na(vaccine_name), "", vaccine_name),
#     FoldCmp = ifelse(fold_cmp == "=", "", fold_cmp),
#     Fold = ifelse(is.na(fold), "", fold),
#     Level =
#       ifelse(
#         resistance_level == "partial-resistance",
#         "partial resistance",
#         resistance_level),
#     Assay = str_to_sentence(ifelse(is.na(assay), "", assay)),
#     Count = cumulative_count,
#     Include = ifelse(include, "Yes", "No"),
#     Control = ifelse(control_variant_name == 'Control', "", control_variant_name)
#   ) %>%
#   select(
#     Author = ref_name,
#     DOI,
#     Source = section,
#     Date = date_added.susc,
#     Plasma,
#     Vaccine,
#     Infection = infection,
#     Position = position,
#     AA = amino_acid,
#     Control,
#     FoldCmp,
#     Fold,
#     Level,
#     Assay,
#     Count,
#     Include
#   ) %>%
#   arrange(
#     Author,
#     Position,
#     AA,
#     Plasma,
#     Vaccine
#   ) %>%
#   styledDT
```

## Spike variants and mutation combinations / mAb neutralization

Columns explained:

- __Author__: Internal unique reference identifier
- __DOI__: DOI
- __Source__: Location of data within reference
- __Date__: Date data added to database.
- __mAb__: mAb name or abbreviation
- __Variant__: Variants of concern (for example, B.1.1.7, B.1.351, P.1), you can find all mutations [here](https://covdb.stanford.edu/page/mutation-viewer/), or combination of spike mutations (for example, S:69del+70del+453F)
- __SpikeMutations__: SARS-CoV2 spike mutation list
- __Control__: Variant used in control group
- __FoldCmp__: Modifier of estimate of fold difference from the control "wildtype" virus: <, >, ~
- __Fold__: Fold difference from the control "wildtype" virus
- __Level__: Susceptibility level
- __Assay__: Default assay is pseudovirus. Assays performed using "authentic" virus are indicated
- __Include__: Entries containing "Exclude" are not displayed on the web

You can copy, download, or print the table using buttons below:


```{r phenotypes-variant-mab}

dfSuscResultsMAb$resistance_level = as.character(dfSuscResultsMAb$resistance_level)

dfSuscResultsMAb %>%
  # filter(num_muts > 1) %>%
  mutate(
    DOI = ifelse(is.na(doi), url, doi),
    mAb = Vectorize(function(x) paste0(x, collapse = "+"))(short_ab_name_with_author_target),
    FoldCmp = ifelse(fold_cmp == "=", "", fold_cmp),
    Fold = ifelse(is.na(fold), "", fold),
    Level = str_to_sentence(
      ifelse(
        resistance_level == "partial-resistance",
        "partial resistance",
        resistance_level)),
    Assay = ifelse(is.na(assay), "", assay),
    Include = ifelse(include, "Yes", "No"),
    Control = ifelse(control_variant_name == 'Control', "", control_variant_name),
    SpikeMutations = ifelse(expandable, spike_muts, variant_name)
  ) %>%
  mutate(
    variant_name = str_replace(variant_name, 'authentic', 'Spike'),
    Control = str_replace(Control, 'authentic', 'Spike')
  ) %>%
  select(
    Author = ref_name,
    DOI,
    Source = section,
    Date = date_added.susc,
    mAb,
    Variant = variant_name,
    SpikeMutations = spike_muts,
    Control,
    FoldCmp,
    Fold,
    Level,
    Assay,
    Include
  ) %>%
  arrange(
    Author,
    Variant,
    mAb
  ) %>%
  styledDT
```

## Spike variants and mutation combinations / plasma neutralization

Columns explained:

- __Author__: Internal unique reference identifier
- __DOI__: DOI
- __Source__: Location of data within reference
- __Date__: Date data added to database
- __Plasma__: CP (convalescent plasma), BNT162b2 (BNT162b2 vaccinated persons), mRNA-1273 (mRNA-1273 vaccinated persons), NVX-CoV2373 (NVX-CoV2373 vaccinated persons). For some CP, author-defined disease severity is provided (e.g., Mild, Hospitalized). For some samples, time since convalescence or vaccination is provided in weeks or months (e.g. 4W, 8M)
- __Vaccine__: Vaccine name
- __Infection__: Infected variant
- __Variant__: Variants of concern (for example, B.1.1.7, B.1.351, P.1), you can find all mutations [here](https://covdb.stanford.edu/page/mutation-viewer/), or combination of spike mutations (for example, S:69del+70del+453F)
- __SpikeMutations__: SARS-CoV2 spike mutation list
- __Control__: Variant used in control group
- __FoldCmp__: Modifier of estimate of fold difference from the control "wildtype" virus: <, >, ~
- __Fold__: Fold difference from the control "wildtype" virus
- __Level__: Susceptibility level
- __Assay__: Default assay is pseudovirus. Assays performed using "authentic" virus are indicated
- __Count__: For some studies, data are presented in aggregate. In this case, the count indicates the number of experiments having the same entries in the Foldcmp and Fold columns
- __Include__: Entries containing "Exclude" are not displayed on the web

You can copy, download, or print the table using buttons below:


```{r phenotypes-variant-plasma}

# dfVariantPlasma = dfSuscResultsPlasma %>%
#   filter(num_muts > 1)
dfVariantPlasma = dfSuscResultsPlasma
dfVariantPlasma$resistance_level = as.character(dfVariantPlasma$resistance_level)
dfVariantPlasma %>%
  mutate(
    DOI = ifelse(is.na(doi), url, doi),
    # Plasma = Vectorize(function(refName, rxName, variantName, ordNum) {
    #   total = nrow(filter(dfVariantPlasma, rx_name == rxName & ref_name == refName & variant_name == variantName))
    #   ifelse(
    #     total == 1,
    #     yes = rxName,
    #     no = sprintf(sprintf("%%s:%%0%dd", 1 + floor(log(total, 10))), rxName, ordNum)
    #   )
    # })(ref_name, rx_name, variant_name, ordinal_number),
    Plasma = rx_name,
    SampleID = ordinal_number,
    Vaccine = ifelse(is.na(vaccine_name), "", vaccine_name),
    FoldCmp = ifelse(fold_cmp == "=", "", fold_cmp),
    Fold = ifelse(is.na(fold), "", fold),
    Level = str_to_sentence(
      ifelse(
        resistance_level == "partial-resistance",
        "partial resistance",
        resistance_level)),
    Assay = str_to_sentence(ifelse(is.na(assay), "", assay)),
    Count = cumulative_count,
    Include = ifelse(include, "Yes", "No"),
    Control = ifelse(control_variant_name == 'Control', "", control_variant_name),
    SpikeMutations = ifelse(expandable, spike_muts, variant_name)
  ) %>%
  mutate(
    variant_name = str_replace(variant_name, 'authentic', 'Spike'),
    Control = str_replace(Control, 'authentic', 'Spike'),
    infection = str_replace(infection, 'authentic', 'Spike')
  ) %>%
  select(
    Author = ref_name,
    DOI,
    Source = section,
    Date = date_added.susc,
    Plasma,
    SampleID,
    Vaccine,
    Infection = infection,
    Variant = variant_name,
    SpikeMutations,
    Control,
    FoldCmp,
    Fold,
    Level,
    Assay,
    Count,
    Include
  ) %>%
  arrange(
    Author,
    Variant,
    Plasma,
    SampleID,
    Vaccine
  ) %>%
  styledDT
```

## Spike mutation Invitro selection

Columns explained:

- __Author__: Internal unique reference identifier
- __DOI__: DOI
- __Source__: Location of data within reference
- __Date__: Date data added to database
- __mAb__: mAb name or abbreviation
- __Position__: Spike amino acid position
- __AAMutation__: amino acid mutation

You can copy, download, or print the table using buttons below:

```{r invitro-selection}
invitroResults = read.invitroResults()
invitroResults = invitroResults %>%
  inner_join(
    dfArticles,
    by = "ref_name",
    suffix = c(".invitro", ".ref")
  )
invitroResults %>%
  mutate(
    DOI = ifelse(is.na(doi), url, doi),
    # mAb = Vectorize(function(x) paste0(x, collapse = "+"))(short_ab_name_with_author_target),
    mAb = rx_name,
    Position=position,
    AAMutation=amino_acid
  ) %>%
  select(
    Author = ref_name,
    DOI,
    Source = section,
    Date = date_added.invitro,
    mAb,
    Position,
    AAMutation
  ) %>%
  arrange(
    Author,
    mAb,
    Position,
    AAMutation
  ) %>%
  styledDT
```


## Spike mutation Invivo selection

Columns explained:

- __Author__: Internal unique reference identifier
- __DOI__: DOI
- __Source__: Location of data within reference
- __Date__: Date data added to database
- __mAb__: mAb name or abbreviation
- __
- __Position__: Spike amino acid position
- __AAMutation__: amino acid mutation

    mAb,
    Dosage=dosage,
    Host = host,
    Patient=patient,
    Sampling=sampling,
    Infection = infection_name,
    SelectedMutations = SpikeMutations,
    TotalPatients = num_patients,
    PatientsWithMut = num_patients_with_mut,
    Note=note


You can copy, download, or print the table using buttons below:

```{r invivo-selection}
invivoResults = read.invivoResults()
invivoResults = invivoResults %>%
  inner_join(
    dfArticles,
    by = "ref_name",
    suffix = c(".invitro", ".ref")
  )
invivoResults %>%
  mutate(
    DOI = ifelse(is.na(doi), url, doi),
    # mAb = Vectorize(function(x) paste0(x, collapse = "+"))(short_ab_name_with_author_target),
    mAb = rx_name,
    Position=position,
    AAMutation=amino_acid
  ) %>%
  select(
    Author = ref_name,
    DOI,
    Source = section,
    Date = date_added.invitro,
    mAb,
    Dosage=dosage,
    Host = host,
    Patient=patient,
    Sampling=sampling,
    Infection = infection_name,
    Position=position,
    AAMutation=amino_acid,
    TotalPatients = num_patients,
    PatientsWithMut = num_patients_with_mut,
    Note=note
  ) %>%
  arrange(
    Author,
    mAb,
  ) %>%
  styledDT
```
