---
title: "Susceptibility data"
output:
  html_document:
    keep_md: yes
    css: "css/main.css"
---

Report generated at: `r format(as.POSIXct(Sys.time(), format = "%y%m%d %H:%M"), "%m/%d/%Y %I:%M %p")` PDT

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
knitr::opts_chunk$set(echo = FALSE)
source("./lib/readers.R", chdir = TRUE)
source("./lib/datatables.R", chdir = TRUE)

TABLEDIR = normalizePath(sprintf('%s/report_tables', .getpwd()))

```

## Variant {.tabset}

### Individual mutation
```{r var-indiv}
indivDT = read.dbTable('summary_variant_indiv.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

### Multiple mutation or variant
```{r var-combo}
multiDT = read.dbTable('summary_variant_combo.csv', tables_dir=TABLEDIR)
styledDT(multiDT)
```

## Indiv mutation vs treatments {.tabset}

### Variant vs Mab
```{r indiv-variant-mab}
indivDT = read.dbTable('summary_variant_indiv_mab.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

### Variant vs CP
```{r indiv-variant-cp}
indivDT = read.dbTable('summary_variant_indiv_cp.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

### Variant vs VP

```{r indiv-variant-vp}
indivDT = read.dbTable('summary_variant_indiv_vp.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

## Combination of mutations vs treatments {.tabset}

### Variant vs Mab
```{r combo-variant-mab}
indivDT = read.dbTable('summary_variant_combo_mab.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

### Variant vs CP
```{r combo-varian-cp}
indivDT = read.dbTable('summary_variant_combo_cp.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

### Variant vs VP

```{r combo-varian-vp}
indivDT = read.dbTable('summary_variant_combo_vp.csv', tables_dir=TABLEDIR)
styledDT(indivDT)
```

## Study {.tabset}

### CP vs study
```{r study-cp}
mabDT = read.dbTable('summary_study_cp.csv', tables_dir=TABLEDIR)
styledDT(mabDT)
```

### VP vs study
```{r study-vp}
mabDT = read.dbTable('summary_study_vp.csv', tables_dir=TABLEDIR)
styledDT(mabDT)
```

### Mab vs study
```{r study-mab}
mabDT = read.dbTable('summary_study_mab.csv', tables_dir=TABLEDIR)
styledDT(mabDT)
```

## Mab {.tabset}

### Mab summary
```{r mab}
mabDT = read.dbTable('summary_mab.csv', tables_dir=TABLEDIR)
styledDT(mabDT)
```

## Plasmas Table {.tabset}

### CP aggregated
```{r cp-aggre}
VP_DT = read.dbTable('summary_cp_aggre.csv', tables_dir=TABLEDIR)
styledDT(VP_DT)
```

### VP aggregated
```{r vp-aggre}
VP_DT = read.dbTable('summary_vp_aggre.csv', tables_dir=TABLEDIR)
styledDT(VP_DT)
```

### Vaccine summary
```{r vaccine}
VP_DT = read.dbTable('summary_vp.csv', tables_dir=TABLEDIR)
styledDT(VP_DT)
```

### Plasma by reference (mutations)
```{r cp_muts}
CP_Muts_DT = read.dbTable('table_plasma_muts.csv', tables_dir=TABLEDIR)
styledDT(CP_Muts_DT)
```

### Plasma by reference (variants)
```{r cp_variants}
CP_Variant_DT = read.dbTable('table_plasma_variant.csv', tables_dir=TABLEDIR)
styledDT(CP_Variant_DT)
```


## Plasmas Figure {.tabset}

### CP and VP summary

```{r cpvp, fig.height=10, fig.retina=4, fig.width=10, message=FALSE, warning=FALSE, echo=FALSE}

plasmaDT = read.dbTable('table_plasma_figure.csv', tables_dir=TABLEDIR) %>%
  mutate(
    study = ifelse(study=='vac', 'Vaccine', 'CP'),
    variant = ifelse(variant == "B.1.429/B.1.427", "B.1.427/429", variant)
    ) %>%
  filter(
    variant != 'L452R' & variant != "B.1.526"
  )

VARIANT = c(
  "B.1.1.7",
  "B.1.351",
  "P.1",
  "B.1.427/9",
  # "B.1.526",
  "N501Y",
  "E484K",
  "K417N",
  "N439K",
  # "L452R",
  "Y453F",
  "∆69/70",
  "∆144"
)

SUSC_VALUE = c("R", "I", "S")
STUDY_TYPE = c("CP", "Vaccine")

plots = list()
i = 1

for (st in STUDY_TYPE) {
    dfPlot = plasmaDT %>%
      filter(study == st) %>%
      mutate(
        variant = factor(variant, VARIANT),
        susc = factor(susc, SUSC_VALUE)
      )

    dfAgg = dfPlot %>%
      group_by(variant, num_study) %>%
      summarise(total=sum(sample_num)) %>%
      mutate(
        total_label = ifelse(
          num_study > 1,
          yes=sprintf('%s studies', num_study),
          no=sprintf('%s study', num_study)
        )

      )

    p <- ggplot(data=dfPlot, aes(x=variant, y=sample_num)) +
      geom_bar(
        aes(fill=susc),
        size=0.2,
        color="#000000",
        stat="identity",
        position='stack'
      ) +
      scale_fill_manual(values = c(
        'R' = "#146aa8",
        'I' = "#7fcbee",
        'S' = "#ffffff"
      )) +
      scale_y_continuous(
        expand=expansion(mult = c(0, .1))
        ) +
      geom_text(
        data=dfAgg,
        aes(y=total, label=total_label),
        size = 4.6,
        vjust = -0.5
        ) +
      theme(
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=20),
        axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=15),
        plot.title = element_text(hjust = 0.5, size=16),
        strip.background = element_blank(),
        strip.text = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, color = 'black')
        ) +
      ylab("# Samples")

    if (st == 'CP') {
      figLabel = "Convalescent plasma"
    }
    else {
      figLabel = "Plasma from vaccinated persons"
    }
    # p = p + ggtitle("Convalescent plasma")
    p = p + annotate(
          "text",
          y= Inf,
          x = Inf,
          label=figLabel,
          size=8,
          vjust=2,
          hjust=1.1)

    plots[[i]] = p
    i = i + 1
}

grid.arrange(grobs = plots)
```